### 2019-05-14 initial/notes.tex
better plotting, phase portraits

To be more precise, $\mu_4$ disappears at
\begin{equation}
    \eta = \eta_c \equiv \p*{\sin^{2/3}I + \cos^{2/3}I}^{-3/2}.
\end{equation}
Thus, we can set $s = \frac{s_c}{\eta_c}$ and $\mu = \mu_4$ and integrate
backwards \autoref{se:prec_avg} backwards in time to determine exactly where
$\mu, s$ cross the separatrix. Physically, we never expect $s < \Omega_1$
though, so the minimum $s_c$ we can use and still expect to see a strong
spin-orbit coupling regime appear is $s_c \geq \Omega_1 \eta_c$.

>>>>

To be more precise, $\mu_4$ disappears at
\begin{equation}
    \eta = \eta_c \equiv \p*{\sin^{2/3}I + \cos^{2/3}I}^{-3/2}.
\end{equation}
Thus, we can set $s = \frac{s_c}{\eta_c}$ and $\mu = \mu_4$ and integrate
backwards \autoref{se:prec_avg} backwards in time to determine $\mu, s$ that are
exactly sufficient for separatrix crossing. Physically, we never expect $s <
\Omega_1$ though, so the minimum $s_c$ we can use and still expect to see a
strong spin-orbit coupling regime appear is $s_c \geq \Omega_1 \eta_c$.
